---
title: "July 20 Update"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

source('simTt_mod.R')
```

### Simulating a Modulated Signal

From Kian's thesis we have the following formula for signals with frequency modulation:

$$X_t = \sum_m{\mu_mcos(2 \pi f_mt + 2 \pi \int_0^t \phi_m (\tau) \space d\tau)} + Z_t$$

Now let $\theta(t) = 2 \pi f_mt + 2 \pi \int_0^t \phi_m (\tau) \space d\tau$. Since $\phi$ and $\theta$ are both polynomials, we can simplify to:

$$\phi(\tau) = \sum_{p=0}^{P}{a_p\tau^p}$$
$$\theta(t) = 2 \pi f_mt + 2 \pi \int_0^t \sum_{p=0}^{P}{a_p\tau^p} \space d\tau$$
$$\theta(t) = 2 \pi f_mt + 2 \pi \int_0^t \sum_{p=0}^{P}{\frac{a_p}{p+1}t^{p+1}}$$

Using these formulas I wrote a function to simulate a modulated signal given a length $N$, number of frequencies $m$, and the maximim degree of polynomial to consider $P$.

```{r simulate}
## Simulating modulated signal
set.seed(1)
Tt = simTt_mod(N = 100, numFreq = 1, P = 2)

## Printing the corresponding summation
print(Tt$fn)
```

```{r plot1, message = FALSE, warning=FALSE, fig.align='center', fig.dim=c(8,5), echo=FALSE}
## Plotting the modulated signal
plot(0:99, Tt$value, type = 'l', lwd = 2, xlab = 'Time', ylab = 'Value', 
     main = 'Simulated Modulated Signal')
grid()
```





