---
title: "Simulation Results"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

```{r reading_data, include = FALSE}
library(dplyr)
library(ggplot2)

sim1 = read.csv('Simulation_Results/sim_1.csv')
sim2 = read.csv('Simulation_Results/sim_2.csv')

colors = c("#F7C65B","#FAAF08","#FA812F","#FA4032","#F92111")
col = colorRampPalette(colors = colors)(100)
```

#### First Set of Simulations:
- All time series of length $N = 1000$.
- Five iterations with each combination of $(P, G)$.
- Comparison of average RMSE, MAE, and MAPE across each Method, $P$, and $G$ combination.
- Used several different parameter combinations for the NNI method. For results, extracted the highest performing NNI model on average within each $(P, G)$ combination.
- Issues with plotting in 'interpTools' so I wrote my own aggregations and plotting formats.

```{r first_sim, message = FALSE, warning=FALSE, fig.align='center', fig.dim=c(8,5), echo=FALSE}

grouped_NNI = sim1 %>% dplyr::group_by(Method, P, G, max_iter, K, n_series, random, method) %>%
                       dplyr::summarise(mae = mean(MAE), 
                                        rmse = mean(RMSE), 
                                        mape = mean(MAPE))

NNI_mae = grouped_NNI %>% dplyr::arrange(mae) %>% 
                          dplyr::group_by(P, G) %>% 
                          dplyr::filter(row_number()==1)
NNI_rmse = grouped_NNI %>% dplyr::arrange(rmse) %>% 
                          dplyr::group_by(P, G) %>% 
                          dplyr::filter(row_number()==1)
NNI_mape = grouped_NNI %>% dplyr::arrange(mape) %>% 
                          dplyr::group_by(P, G) %>% 
                          dplyr::filter(row_number()==1)

imp_mae = rbind(sim2 %>% dplyr::group_by(Method, P, G) %>% dplyr::summarize(mae = mean(MAE)), 
                NNI_mae %>% dplyr::select(Method, P, G, mae))
imp_rmse = rbind(sim2 %>% dplyr::group_by(Method, P, G) %>% dplyr::summarize(rmse = mean(RMSE)), 
                NNI_rmse %>% dplyr::select(Method, P, G, rmse))
imp_mape = rbind(sim2 %>% dplyr::group_by(Method, P, G) %>% dplyr::summarize(mape = mean(MAPE)), 
                NNI_mape %>% dplyr::select(Method, P, G, mape))

desired_order = c("HWI", "NNI", "EWMA", "LI")
imp_mae$Method = factor(as.character(imp_mae$Method), levels = desired_order)
imp_mae <- imp_mae[order(imp_mae$Method),]
imp_rmse$Method = factor(as.character(imp_rmse$Method), levels = desired_order)
imp_rmse <- imp_rmse[order(imp_rmse$Method),]
imp_mape$Method = factor(as.character(imp_mape$Method), levels = desired_order)
imp_mape <- imp_mape[order(imp_mape$Method),]
```


```{r first_sim2, message = FALSE, warning=FALSE, fig.align='center', fig.dim=c(8,5), echo=FALSE}
ggplot(imp_mae, aes(P, G, fill = mae)) +
  geom_tile(color = "gray95",lwd = 0.5, linetype = 1) +
  facet_grid(~ Method) +
  labs(title = 'Simulation Results with N = 1000 (Avg. MAE)', 
       x = "Missing Proportion (P)", 
       y = "Gap Width (G)", 
       fill = 'MAE') +
  scale_fill_gradientn(colours = col, values = c(0,1)) + 
  guides(fill = guide_colourbar(label = FALSE, ticks = FALSE)) +
  geom_text(aes(label = round(mae, 3)), color = "white", size = 3) +
  theme_minimal()
```

```{r first_sim3, message = FALSE, warning=FALSE, fig.align='center', fig.dim=c(8,5), echo=FALSE}
ggplot(imp_rmse, aes(P, G, fill = rmse)) +
  geom_tile(color = "gray95",lwd = 0.5, linetype = 1) +
  facet_grid(~ Method) +
  labs(title = 'Simulation Results with N = 1000 (Avg. RMSE)', 
       x = "Missing Proportion (P)", 
       y = "Gap Width (G)", 
       fill = 'RMSE') +
  scale_fill_gradientn(colours = col, values = c(0,1)) + 
  guides(fill = guide_colourbar(label = FALSE, ticks = FALSE)) +
  geom_text(aes(label = round(rmse, 3)), color = "white", size = 3) +
  theme_minimal()
```

```{r first_sim4, message = FALSE, warning=FALSE, fig.align='center', fig.dim=c(8,5), echo=FALSE}
ggplot(imp_mape, aes(P, G, fill = mape)) +
  geom_tile(color = "gray95",lwd = 0.5, linetype = 1) +
  facet_grid(~ Method) +
  labs(title = 'Simulation Results with N = 1000 (Avg. MAPE)', 
       x = "Missing Proportion (P)", 
       y = "Gap Width (G)", 
       fill = 'MAPE') +
  scale_fill_gradientn(colours = col, values = c(0,1)) + 
  guides(fill = guide_colourbar(label = FALSE, ticks = FALSE)) +
  geom_text(aes(label = round(mape, 1)), color = "white", size = 3) +
  theme_minimal()
```

\newpage


#### Second Set of Simulations:
- All time series of length $N = 1000$.
- 10 iterations with each combination of $(P, G)$ and more options for $P$ and $G$.
- Comparison of average RMSE, MAE, and MAPE across each Method, $P$, and $G$ combination.
- Too many issues with the HWI error (same one as last week) so I had to omit it from this set of simulations.
- Used a single set of parameters for the NNI based on the dominant parameters in the first set of simulations (Standouts: 'random' == FALSE, 'method' == noise, larger amount of training data).
- Issues with plotting in 'interpTools' so I wrote my own aggregations and plotting formats.


```{r second_sim, message = FALSE, warning=FALSE, fig.align='center', fig.dim=c(8,5), echo=FALSE}


```


```{r second_sim2, message = FALSE, warning=FALSE, fig.align='center', fig.dim=c(8,5), echo=FALSE}

```

```{r second_sim3, message = FALSE, warning=FALSE, fig.align='center', fig.dim=c(8,5), echo=FALSE}

```

```{r second_sim4, message = FALSE, warning=FALSE, fig.align='center', fig.dim=c(8,5), echo=FALSE}

```




#### Third Set of Simulations:
- All time series of length $N = 1000$.
- Instead of simulating time series with periodic components, only using the 'simWt' function from interpTools which uses 'arima.sim' to generate stationary noise. 
- 10 iterations with each combination of $(P, G)$ and more options for $P$ and $G$.
- Comparison of average RMSE, MAE, and MAPE across each Method, $P$, and $G$ combination.
- Too many issues with the HWI error (same one as last week) so I had to omit it from this set of simulations.
- Used a single set of parameters for the NNI based on the dominant parameters in the first set of simulations (Standouts: 'random' == FALSE, 'method' == noise, larger amount of training data).
- Issues with plotting in 'interpTools' so I wrote my own aggregations and plotting formats.

